\documentclass[11pt,a4paper]{report}
\usepackage{thesis}

\usepackage{geometry}
\geometry{tmargin=1in,rmargin=1in}

\pdfoutput=1

\setcounter{secnumdepth}{3}

% Put here some packages required or/and some personnal commands
\usepackage{ptdr-definitions}

\usepackage{calc}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{topcapt}
\usepackage{lineno}
\usepackage{subfig}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{longtable}
\usepackage{appendix}
\usepackage{multirow}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{slashed}
\usepackage{bookmark}
%\usepackage{subcaption}

\bookmarksetup{
  numbered,
}

\usepackage{bm}
\usepackage{rotating}

\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

% Local definitions.
\newcommand{\editComment}[1]{{\color{Red} #1}} % Indicates who is organising each section.

\newcommand{\ttbar}{\ensuremath{t\overline{t}}\xspace} % t-tbar
\newcommand{\ttZ}{$\text{t}\overline{\text{t}}\textrm{Z}$}
\newcommand{\ttbarZ}{$\text{t}\overline{\text{t}}\textrm{Z}$}
\newcommand{\ttW}{$\text{t}\overline{\text{t}}\textrm{W}$}
\newcommand{\ttbarW}{$\text{t}\overline{\text{t}}\textrm{W}$}
\newcommand{\ttH}{$\text{t}\overline{\text{t}}\textrm{H}$}
\newcommand{\ttbarH}{$\text{t}\overline{\text{t}}\textrm{H}$}
\newcommand{\ttbarGamma}{$\text{t}\overline{\text{t}}\gamma$}
\newcommand{\ttbarY}{$\text{t}\overline{\text{t}}\gamma$}
\newcommand{\ttY}{$\text{t}\overline{\text{t}}\gamma$}
\newcommand{\ttV}{$\text{t}\overline{\text{t}}\textrm{V}$}
\newcommand{\ttbarV}{$\text{t}\overline{\text{t}}\textrm{V}$}
 
% units
\newcommand{\T}{\unit{T}}
\newcommand{\ms}{\unit{ms}}
\newcommand{\ns}{\unit{ns}}
\newcommand{\mrad}{\unit{mrad}}
\newcommand{\Gbps}{\unit{Gb\hspace{-0.16em}/\hspace{-0.08em}s}}
\newcommand{\Tbps}{\unit{Tb\hspace{-0.16em}/\hspace{-0.08em}s}}
\newcommand{\Hz}{\unit{Hz}}
\newcommand{\kHz}{\unit{kHz}}
\newcommand{\MHz}{\unit{MHz}}
\newcommand{\GHz}{\unit{GHz}}
 
% Don't use ``c'' in GeV units, to be consistent with TDR.
\renewcommand{\GeVc}{\GeV}
\renewcommand{\GeVcc}{\GeV}

% Command definitions.
\newcommand{\pT}{\ensuremath{p_{\mathrm{T}}}\xspace}
\newcommand{\sector}{sector\xspace}
\newcommand{\segment}{\sector}
\newcommand{\qpt}{\ensuremath{q\hspace{-0.08em}/\hspace{-0.08em}\pt}\xspace}
\newcommand{\rphi}{$r$-$\varphi$\xspace}
\newcommand{\rz}{$r$-$z$\xspace}
%\newcommand{\PU}{pile-up\xspace}
\newcommand{\PU}{PU\xspace} % PU is now defined in Section 1
\newcommand{\OT}{outer tracker\xspace}
\renewcommand{\HT}{Hough Transform\xspace} % redefinition of CMS command for total transverse energy ...
\newcommand{\KF}{Kalman Filter\xspace}
\newcommand{\LR}{Linear Regression\xspace}
\renewcommand{\DR}{Duplicate Removal\xspace}
\newcommand{\MS}{multiple scattering\xspace}
\newcommand{\mat}[1]{\mathbf{#1}}
\newcommand{\combine}{\texttt{combine}}

\linespread{1.25} %% 1.5 line spacing as nominal is 1.2, ergo 1.2*1.25=1.5
\linenumbers


%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%% 

% >> Title: please make sure that the non-TeX equivalent is in PDFTitle below
\begin{document}
\title{
Search for the Production of a Single Top Quark in association with a Z Boson at the LHC 
}

\author{Alexander D. J. Morton}

\maketitle

\abstract{
A search for the production of a single top quark in association with a Z boson and an additional jet using data from proton-proton collisions at $\sqrt{s} = 13\TeV$ collected by the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider is presented.
This is a rare process that is predicted by the Standard Model 
This search focussed on identifying the final state containing two leptons from the Z boson decay, two jets from the decay of the W boson produced by the top quark decay, a b-jet from the top quark decay and a recoil jet.
The signal was dominated by backgrounds involving a real Z boson or two promptly produced leptons consist with a Z boson decay, primarily Z+jet and top quark pair production.
As such, a Boosted Decision Tree was used to enhance the separation between the signal and background processes.
Using a dataset corresponding to 35.9\fbinv, a production cross section of $292.6_{-126.9}^{+100.2}$ fb and $222.5_{-94.9}^{+90.2}$ fb was measured for this process when the Z boson decays into a pair of electron and muons, respectively.
This corresponds to an observed (expected) signal significance of $2.722\sigma$ ($0.460\sigma$) and $2.501 \sigma$ ($0.544\sigma$), respectively, compared to the background-only hypothesis.
These measurements are consistent within two standard deviations of the Standard Model prediction and the measurements made using the final state where the Z boson and W boson decay leptonically.

The CMS experiment's new tracking detector at the High-Luminosity Large Hadron Collider will require the ability to reconstruct all charged tracks with transverse momentum greater than 2-3\GeV within 4\mus so that they can be used in the Level-1 trigger decision.
One of the proposed track finders is an FPGA-based based solution using a fully time-multiplexed architecture, where track candidates are reconstructed using a projective binning algorithm based on the Hough Transform.
Studies into the suitability of a linearised $\chi^{2}$ algorithm for fitting track parameters were undertaken and it was found that its performance was inferior compared to that of a combinatorial \KF fitter.
The impact of reducing the minimum track transverse momentum from 3\GeV to 2\GeV on the proposed system was also evaluated.
The resulting degradation of of performance was found to be recoverable by improving the handling of multiple scattering in the track finding and fitting algorithms.
}

\chapter*{Declaration of Authorship} \label{sec:declaration}
The work described in this thesis was conducted solely by the author, except where collaboration with others occurred as stated within the text, during their time as a candidate for a research degree at this University.

Figures from CMS publications are labelled ``CMS'' or``CMS Simulation'', when the material only includes simulated events.
Figures labelled ``CMS Preliminary'' are from an unpublished or preliminary public CMS publication.
All figures taken from external sources are referenced throughout this thesis.

The work described in Chapter~\ref{chapter:tk-upgrade} formed part of the author's contributions to \emph{TMTT} project's development of the proposed track finding system described within that chapter.
To produce the results presented in Chapter~\ref{chapter:tk-upgrade}, the author worked in collaboration with other members of the \emph{TMTT} project who predominantly based at the University of Bristol, Brunel University London, Imperial College London, STFC Rutherford Appleton Laboratory and the Karlsruhe Institute of Technology.
In addition to the studies described in that chapter, author's other contributions to the \emph{TMTT} project included various robustness studies and the development of the software framework used to integrate and evaluate the performance of track fitting algorithms

The author has collaborated with other members of the High Energy Physics group at Brunel University London to produce the physics analysis presented in this thesis.
The principle contributions the author made towards the analysis are described in Chapters~\ref{chapter:data-mc},~\ref{chapter:tzq-search},~\ref{chapter:bkg} and~\ref{chapter:results}.
The work involving the development and optimisation of the multivariate analysis technique and statistical analysis technique that was used was principally undertaken by other members of the High Energy Physics group and is described in Chapters~\ref{chapter:results} and~\ref{chapter:results}, respectively.


No work contained within this thesis has not been submitted to this or any other university as part of the requirement for any qualification.
When the published work of others has been consulted, it has been clearly attributed within the text.


\clearpage
\newpage

\chapter*{Acknowledgements} \label{sec:acknowledgments}
This thesis would not have been possible without the time, help, thoughts, and advice of many people.

First and foremost, I would like to thank my supervisor \textit{Joanne Cole} for her continual support, guidance and advice over the course of the last four years.
I am not sure how I can ever express my gratitude for her ability to always find time for me and for the uncountable number of times she has corrected this thesis.
I would also like to thank my second supervisor \emph{Peter Hobson} and my research development advisor \emph{David Smith} for their 

I would like to thank \textit{Catherine Mackay} and \textit{Corin Hoad} in particular for their work on the statistical aspects of the tZq analysis presented in this thesis.
Without both of their efforts I suspect that the analysis would not be in as mature a state as it currently is.
My thanks go to \textit{Ivan Reid} whose timely technical support and tolerance of my high bandwidth usage on the Brunel HEP group's computing resources made the work presented in this thesis possible.

I would also like to thank all those I've worked with throughout the UK CMS Collaboration and during my time at CERN, especially those from the CMS Single Top Physics community and the \emph{TMTT} collaboration.
In particular I would like to thank \textit{Andrew Rose} and \textit{Mark Pesaresi} for not only their advice throughout the last four years, but also for being responsible for my interest in \emph{High Energy Physics}in the first place.
A special thanks is warranted to  \textit{Douglas Burns}, \textit{Fionn Ball}, \textit{Rachel Hyneman} and \textit{Seth Zenz} for the many enjoyable (and educational) lunches and cups of coffee we've had from across the globe.

I would like to thank all of my friends and family for their support through the years.
\textit{Darije \v{C}ustovi{c}}, \textit{Diana Lucaci}, \textit{Reuben Hill}, and \textit{Thore Bucking}; for not only occasionally providing me with a place to stay when I needed it, but whose interest in my work, no matter how seemingly banal, re-motivated me when I needed it most.
I am incredibly grateful to my Mother and Father and \textit{Annabel Shaw}; without your constant support and encouragement throughout the years, especially during the writing up of this thesis, I doubt I would have made it this far.

Finally, but most importantly, I would like to thank \textit{Peter Hobson} and the Science and Technologies Facilities Council.
Without them, I would not have had the privilege of being able to embark on this work. 

\tableofcontents
\listoftables
\listoffigures

\input{tex/introduction.tex}

\input{tex/sm.tex}

\input{tex/lhc.tex}

\input{tex/tk-upgrade.tex}

\input{tex/data-mc.tex}

\input{tex/tzq-search.tex}

\input{tex/tzq-systematics.tex}

\input{tex/results.tex}

\input{tex/conclusion.tex}

\begin{appendices}
\input{tex/appendix_maths.tex}
%\input{tex/appendix_plots.tex}
\input{tex/appendix_bdt.tex}
\end{appendices}

\bibliographystyle{JHEP}
\bibliography{admorton_thesis}
 
\end{document}

